---
title: "First Attempts at JSON Parsing Using Package Listviewer"
author: "Barry DeCicco"
date: "8/8/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## **Listviewer**

### Listviewer is a package for the diplay of lists. In this example I am using the jsonedit() function to create a tree view of lists.

```{r set-up - load libraries and data sets}

library(tidyverse)
library(listviewer)
library(jsonlite)

gapminder <- readRDS("Data/gapminder.rds")

```

### Tree View of Data Frame

#### Since a data frame is a list of vectors, the jsonedit() will display a tree view:

```{r tree view of gapminder, echo=TRUE}

head(gapminder)

jsonedit(listdata=gapminder)

```

#### **In the original HTML file, you could click on the arrows above, and display more information.**

```{r INSERT NAME HERE, echo=TRUE}


```

### From the example in help - this lists all of the parameters contained in/set by par():

```{r Look at par(), echo=TRUE}


jsonedit(listdata=par())

```

### Examining the structure of the results of summary():

```{r Summary, echo=TRUE}

summary_gapminder <- summary(gapminder)
class(summary_gapminder)
jsonedit(listdata=summary_gapminder)

```

#### **Again, in the original HTML file, you could click on the arrows above, and display more information about the summary.**


### Apparently the str() function command  is of class NULL; jsonedit() returns an empty object:

```{r Structure, echo=TRUE}

structure_gapminder <- str(gapminder)
class(structure_gapminder)
jsonedit(listdata=structure_gapminder)


```

### List example from: http://www.r-tutor.com/r-introduction/list

### It turns out that jsonedit() returns a list, which can **not** be coerced into a data frame (at least from what I know of R):

```{r list example, echo=TRUE}

n = c(2, 3, 5) 
s = c("aa", "bb", "cc", "dd", "ee") 
b = c(TRUE, FALSE, TRUE, FALSE, FALSE) 
x = list(n, s, b, 3)   # x contains copies of n, s, b 

class(x)
head(x)

jsonedit_list <- jsonedit(listdata=x) 
  
class(jsonedit(jsonedit_list))

jsonedit_list

```

### jsonedit() returns a list, which can be coerced to a data frame using **unlist()**:

```{r list convert to data frame, echo=TRUE}


jsonedit_df <- jsonedit_list %>%
  unlist(.)                     %>%
  as.data.frame()  
  
class(jsonedit_df)

```


```{r print head of converted data frame, echo=TRUE}

jsonedit_df

```